\documentclass[a4paper,11pt]{article}
\usepackage{latexsym, fullpage, titlesec, marvosym, enumitem, hyperref, fancyhdr, tabularx, fontawesome}
\usepackage[usenames,dvipsnames]{color}

% 页面布局
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% 链接样式
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% 章节格式
\titleformat{\section}{\scshape\large\raggedright}{}{0em}{}[\titlerule]

% 自定义列表环境
\newenvironment{resumeList}{\begin{itemize}[leftmargin=*,label={}]}{\end{itemize}}
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeEntry}[4]{
  \item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    #3 & #4 \\
  \end{tabular*}
}

\begin{document}

% 个人信息
\begin{center}
    {\Huge\bfseries Zhaoting Lv} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} +86 138-0343-9355 $|$ 
    \faAt \hspace{.5pt} \href{mailto:lvzting0717@163.com}{lzting0717@163.com} $|$ 
    \faMapMarker \hspace{.5pt} MeiLinWan, Wanbailin District, Taiyuan, Shanxi, China 
\end{center}

% 教育背景
\section{EDUCATION}
\begin{resumeList}
    \resumeEntry{QILU UNIVERSITY OF TECHNOLOGY}
    {Jinan, Shandong, China}
    {Bachelor of Science in Computer Science and Technology}
    {Sep 2021 -- Jun 2025}
    
    \resumeItem{GPA: 3.4/5.0 \qquad CET6: 516} 
    \resumeItem{Key Courses: Data Structures (88), Computer Organization (89), Advanced Math (93), Linear Algebra (97), Probability (91), Numerical Analysis (93)}
\end{resumeList}

% 项目经历
\section{PROJECTS}
\begin{resumeList}
    \resumeEntry{Online Food Ordering Management System}
    {}
    {Spring Boot (Java Backend), MyBatis-Plus, Spring Security}
    {}

    \resumeItem{Built system using Spring Boot with MVC, enhancing maintainability.}
    \resumeItem{Integrated Spring Security and Kerberos for enterprise-level SSO authentication, addressing security risks in plaintext password storage.}

    \resumeEntry{Tourism Recommendation System}
    {}
    {Scrapy, Django, PyCharts}
    {}

    \resumeItem{Used Scrapy + Asyncio + Aiohttp for concurrent scraping, improving speed by 40\%.}
    \resumeItem{Implemented Django + PyCharts for data visualization and enhanced user interaction.}

    \resumeEntry{Building Sustainability Assessment Research}
    {HELIYON (IF: 3.4)}
    {Third Author, DOI: 10.1016/j.heliyon.2024.e32151}
    {Jun 2024}

    \resumeItem{Applied PCA to cluster 47 indicators, validating 7 secondary classifications.}
    \resumeItem{Optimized system, reducing redundant data by 17\%.}
\end{resumeList}

% 工作经验
\section{WORK EXPERIENCE}
\begin{resumeList}
    \resumeEntry{Dareway Software CO., LTD.}
    {Jinan, Shandong, China}
    {Java Development Intern}
    {Jun 2023 -- Aug 2023}

    \resumeItem{Developed core modules for "Smart Government Affairs Platform," focusing on user permission management.}
    \resumeItem{Used Spring Boot, MyBatis, Vue.js for microservices, resolving 25+ bugs with a 95\% code merge pass rate.}
    \resumeItem{Optimized government data processing module, improving efficiency by 30\%.}
    \resumeItem{Implemented an ECharts dashboard for data visualization, successfully integrated into the system.}
\end{resumeList}

% 奖项与荣誉
\section{AWARDS \& HONORS}
\begin{resumeList}
    \resumeEntry{China Undergraduate Mathematical Contest}
    {Shandong Division}
    {Second Prize}
    {Oct 2024}

    \resumeItem{Competed against 5,000+ students in Shandong Province.}
    \resumeItem{Practiced 20+ hours weekly for 3 months, focusing on advanced calculus and linear algebra.}
    \resumeItem{Developed a new integral solving method, increasing efficiency by 30\%.}
    \pagebreak
    \resumeEntry{Second-Class Scholarship}
    {Qilu University of Technology}
    {}
    {2021-2022}

    \resumeItem{Awarded to the top 15\% of students based on academics and extracurriculars.}
    \resumeItem{Led programming team, managed version control, and developed core functionalities for team projects.}
    \resumeEntry{C1 Driver's License}
{China}
{}
{2023}
\end{resumeList}

% 技能
\section{TECHNICAL SKILLS}
\begin{resumeList}
    \resumeItem{Proficient in Linux, Git/GitHub, and collaborative development.}
    \resumeItem{Experienced in JWT, Kerberos, and encryption algorithms like DES.}
    \resumeItem{Expert in web scraping (Scrapy, BeautifulSoup, Selenium), with anti-scraping techniques such as User-Agent spoofing, IP proxy pools, CAPTCHA recognition (Tesseract OCR), and request frequency control.}
\end{resumeList}

\end{document}
