\documentclass[a4paper,11pt]{article}
\usepackage{latexsym, fullpage, titlesec, marvosym, enumitem, hyperref, fancyhdr, tabularx, fontawesome}
\usepackage[usenames,dvipsnames]{color}
\pagestyle{fancy}
\fancyhf{} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\scshape\large\raggedright}{}{0em}{}[\titlerule]

% Custom environment and commands
\newenvironment{resumeList}{\begin{itemize}[leftmargin=*,label={}]}{\end{itemize}}
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeEntry}[4]{
  \item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    #3 & #4 \\
  \end{tabular*}
}

\begin{document}
% Personal Information
\begin{center}
    {\Huge\bfseries L\text{"u} Zhaoting} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} +86 138-0343-9355 $|$ \faAt \hspace{.5pt} \href{mailto:lvzting0717@163.com}{lzting0717@163.com} $|$ \faMapMarker \hspace{.5pt} Taiyuan, Shanxi, China 
\end{center}

% Education
\section{Education}
\begin{resumeList}
    \resumeEntry{Qilu University of Technology (Shandong Academy of Sciences)}{Shandong, China}{Bachelor of Computer Science and Technology}{Sep 2021 -- Jun 2024}
    \begin{resumeList}
        \resumeItem{Key Courses: Data Structures (88), Computer Organization (89), Linux Programming Basics (88), Advanced Mathematics (85), Linear Algebra (97), Probability and Mathematical Statistics (91), Discrete Mathematics (85), Numerical Analysis (93), Machine Learning and Pattern Recognition (85)}
        \resumeItem{CET6 (516) | National College Mathematics Competition (Shandong Division, Second Prize) | College Second-Class Scholarship | C1 Driver's License}
    \end{resumeList}
\end{resumeList}

% Projects
\section{Projects}
\begin{resumeList}
    \resumeEntry{Meal Ordering Management System Based on Spring Boot}{}{Spring Boot (Java Backend), MyBatis-Plus, Spring Security}{}
    \begin{resumeList}
        \resumeItem{Built the system using Spring Boot, following the MVC design pattern to improve development efficiency and maintainability.}
        \resumeItem{Integrated Spring Security + Kerberos for enterprise-level SSO authentication, enhancing system security.}
    \end{resumeList}
    \resumeEntry{8-bit ALU Design}{}{Quartus II, HDL, TD-CMA Experimental Box}{}
    \begin{resumeList}
        \resumeItem{Optimized the adder with a fast carry chain, achieving efficient addition/subtraction and logical operations.}
        \resumeItem{Designed circuit diagrams using Quartus II, wrote HDL code, and tested it on the TD-CMA experimental box.}
    \end{resumeList}
    \resumeEntry{Tourism Recommendation System Based on Django}{}{Scrapy, Django, PyCharts}{}
    \begin{resumeList}
        \resumeItem{Implemented high-performance web scraping using Scrapy + Asyncio + Aiohttp concurrent crawler.}
        \resumeItem{Developed a Django web application with PyCharts for interactive data visualization.}
    \end{resumeList}
    \resumeEntry{Research on Building Sustainability Assessment}{HELIYON (IF: 3.4)}{Third Author}{2024}
    \begin{resumeList}
        \resumeItem{Applied PCA to cluster 47 indicators, validating the rationality of 7 secondary indicator classifications.}
        \resumeItem{Identified key indicators and optimized the indicator system, reducing redundant data by 17\%.}
    \end{resumeList}
\end{resumeList}

% Professional Skills
\section{Professional Skills}
\begin{resumeList}
    \resumeItem{Proficient in Git/GitHub and experienced in collaborative development.}
    \resumeItem{Familiar with Linux operations and capable of writing Shell scripts.}
    \resumeItem{Skilled in Java, familiar with JUC concurrent programming, lock mechanisms, and thread pool principles.}
    \resumeItem{Experienced with Spring, SpringMVC, SpringBoot, and MyBatis, with knowledge of Spring Cloud integration and Spring Boot execution processes.}
    \resumeItem{Knowledgeable in authentication mechanisms such as JWT and Kerberos, and fundamental concepts of symmetric/asymmetric encryption algorithms like DES.}
    \resumeItem{Experienced in MySQL, proficient in index optimization, transaction management, and database partitioning strategies.}
\end{resumeList}

\end{document}
