\documentclass[a4paper,11pt]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage{latexsym,titlesec,marvosym,enumitem,hyperref,fancyhdr,tabularx,fontawesome,microtype,xcolor}
\hypersetup{colorlinks, urlcolor=blue}
\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\flushbottom

\renewcommand{\baselinestretch}{1.03}\selectfont
\setlength{\parskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0in}

\setlist[itemize]{leftmargin=*, label=\textbullet{}, itemsep=2pt, topsep=3pt}

\titleformat{\section}{\scshape\normalsize\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\newenvironment{resumeList}{\begin{itemize}[leftmargin=*, label=\textbullet{}, itemsep=2pt]}{\end{itemize}}
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeEntry}[4]{%
  \textbf{#1} \hfill #2 \\
  \small #3 \hfill #4
  \vspace{-3pt}
}

\begin{document}
\normalsize  

\begin{center}
    {\bfseries\huge Zhaoting Lv} \\[3pt]
    \small
    \faMobile\,+86 138-0343-9355 \quad $|$ \quad 
    \faAt\,\href{mailto:lvzting0717@163.com}{lzting0717@163.com} \quad $|$ \quad 
    \faMapMarker\,MeiLinWan, Wanbailin District, Taiyuan, Shanxi, China
\end{center}

\section{EDUCATION}
\resumeEntry{QILU UNIVERSITY OF TECHNOLOGY}{Jinan, Shandong, China}
{B.S. in Computer Science and Technology}{Sep 2021 -- Jun 2025}
\begin{resumeList}
    \resumeItem{GPA: 3.4/5.0 \quad CET6: 516} 
    \resumeItem{Key Courses: Data Structures (88), Computer Organization (89), Advanced Math (93), Linear Algebra (97), Probability (91), Numerical Analysis (93)}
\end{resumeList}

\section{PROJECTS}
\resumeEntry{Online Food Ordering System}{Database Course Design}
{Spring Boot, MyBatis-Plus, Spring Security}{May 2022}
\begin{resumeList}
    \resumeItem{Developed with Spring Boot and MVC, enhancing maintainability.}
    \resumeItem{Integrated Spring Security and Kerberos for SSO authentication, addressing password security risks.}
\end{resumeList}

\resumeEntry{Tourism Recommendation System}{}{Scrapy, Django, PyCharts}{Sep 2024}
\begin{resumeList}
    \resumeItem{Used Scrapy with Asyncio and Aiohttp for concurrent scraping, improving efficiency by 40\%.}
    \resumeItem{Implemented Django with PyCharts for data visualization and better user interaction.}
\end{resumeList}

\resumeEntry{Building Sustainability Research}{HELIYON (IF: 3.4)}
{Third Author, DOI: 10.1016/j.heliyon.2024.e32151}{Jun 2024}
\begin{resumeList}
    \resumeItem{Applied PCA to cluster 47 indicators, validating 7 secondary classifications.}
    \resumeItem{Optimized system to reduce redundant data by 17\%.}
\end{resumeList}

\section{INTERNSHIP}
\resumeEntry{Dareway Software CO., LTD.}{Jinan, Shandong, China}
{Java Backend Development Intern}{Jun 2023 -- Aug 2023}
\begin{resumeList}
    \resumeItem{Developed core modules for "Smart Government Affairs Platform," focusing on user permission management.}
    \resumeItem{Used Spring Boot, MyBatis, and Vue.js in a microservices setup, fixing 25+ bugs with a 95\% merge rate.}
    \resumeItem{Optimized data processing module, boosting efficiency by 30\%.}
    \resumeItem{Created an ECharts dashboard integrated into the system for data visualization.}
\end{resumeList}

\section{HONORS}
\renewcommand{\arraystretch}{1.3}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    Second-Class Scholarship, Qilu University of Technology & 2022 \\
    C1 Driver's License & 2023 \\
    Second Prize, China Undergraduate Mathematical Contest (Shandong) & 2024 \\
\end{tabular*}
\renewcommand{\arraystretch}{1.0}

\section{TECHNICAL SKILLS}
\begin{resumeList}
    \resumeItem{Proficient: Linux, Git/GitHub, collaborative development.}
    \resumeItem{Experienced: JWT, Kerberos, encryption algorithms (DES).}
    \resumeItem{Skilled: Web scraping (Scrapy, BeautifulSoup, Selenium); Anti-scraping (User-Agent spoofing, IP proxy pools, CAPTCHA recognition with T
